---
title: "R Notebook"
output: html_notebook
---

# Import Libs 
```{r}
#library(ggplot2)
#library(patchwork)
library(neuroCombat)
library(lsr)
library(car)
#library(ggcorrplot)
library(factoextra)
library(reshape2)
library(fastICA)
library(tidyverse)
#library(userfriendlyscience)
library(lmerTest)
library(readxl)
library(MuMIn)
library(RobStatTM)
library(robust)
```

# Import data 
Import data and then initially split the data into LTLE 
```{r}
data <- read_excel("/Users/lawrencebinding/Desktop/projects/Epilepsy/p1802Memory/Fibre_bundle_paper/final_analysis/AllPatients_Public_anon.xlsx", na = c("NaN", "NAN"))
data_LTLE <- data[data$TLE_side == "LTLE", ]
```

# Check for scanner differences 
```{r}
#Fornix 
t.test(Tractography_FNX ~ Scanner, data=data_LTLE)
t.test(Postop_vol_FNX ~ Scanner, data=data_LTLE)

#Ventral Cingulum 
t.test(Tractography_vCing ~ Scanner, data=data_LTLE)
t.test(Postop_vol_vCing ~ Scanner, data=data_LTLE)

```

## Fornix Correction
```{r}
#Put data for combat in a separate variable 
data_for_combat = t(data_LTLE[,c("Postop_vol_FNX","Tractography_FNX")])
Scanner = t(data_LTLE[,c('Scanner')])

#Index the nans 
cols_with_nan <- apply(data_for_combat, 2, function(col) any(is.na(col)))

#Remove NaNs 
data_for_combat_clean <- data_for_combat[, !cols_with_nan]
Scanner_clean <- Scanner[, !cols_with_nan]

#Run neurocombat 
data_harm <- neuroCombat(dat=data_for_combat_clean, batch=Scanner_clean)
data_harm = data.frame(t(data_harm$dat.combat))

#Output the data 
data_LTLE$Postop_vol_FNX_harm <- NA  
data_LTLE$Postop_vol_FNX_harm[!cols_with_nan] <- data_harm$Postop_vol_FNX
data_LTLE$Tractography_FNX_harm <- NA  
data_LTLE$Tractography_FNX_harm[!cols_with_nan] <- data_harm$Tractography_FNX
```

# Scale data 
```{r}
# Preop tracts  
data_LTLE$Tractography_vCing_scaled <- as.vector(scale(data_LTLE$Tractography_vCing))
data_LTLE$Tractography_FNX_scaled <- as.vector(scale(data_LTLE$Tractography_FNX_harm))
# Postop volume 
data_LTLE$Postop_vol_FNX_scaled <- as.vector(scale(data_LTLE$Postop_vol_FNX_harm))
data_LTLE$Postop_vol_vCing_scaled <- as.vector(scale(data_LTLE$Postop_vol_vCing))
#Covariates 
data_LTLE$ResectinMask_Scaled <- as.vector(scale(data_LTLE$ResectionvMask))
#Neuropsychology
data_LTLE$ListA15_preZ_scaled <- as.vector(scale(data_LTLE$List15_preZ))
data_LTLE$ListA6_preZ_scaled <- as.vector(scale(data_LTLE$ListA6_preZ))
```

# RCI Generation
## Verbal Encoding 
```{r}
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#3 months 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
summary( List15_3mZ_change <- lmrobdetMM(List15_3mZ_change ~ Age + ResectinMask_Scaled +  List15_preZ  , data=data_LTLE,na.action= na.omit))

# Make a copy of residuals
residuals_bin <- List15_3mZ_change$residuals

# Set all elements to 0
residuals_bin <- rep(0, length(residuals_bin))


# Set elements to 1 where residuals are greater than 1.5 standard deviations
residuals_bin[List15_3mZ_change$residuals <= (quantile(List15_3mZ_change$residuals,0.20))] <- -1

# Set elements to -1 where residuals are less than -1.5 standard deviations
residuals_bin[List15_3mZ_change$residuals >= (quantile(List15_3mZ_change$residuals,0.80))] <- 1

# Get the index of non-missing values in the 'List15_3mZ_change' column
non_missing_index <- !is.na(data_LTLE$List15_3mZ_change)

# Place the residuals back into the dataframe at the non-missing index
data_LTLE$List15_3mZ_change_residuals_bin <- NA  # Initialize a new column for residuals
data_LTLE$List15_3mZ_change_residuals_bin[non_missing_index] <- residuals_bin
data_LTLE$List15_3mZ_change_residuals <- NA  # Initialize a new column for residuals
data_LTLE$List15_3mZ_change_residuals[non_missing_index] <- List15_3mZ_change$residuals

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#12 months 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
summary( List15_12mZ_change <- lmrobdetMM(List15_12mZ_change ~ Age + ResectinMask_Scaled +  List15_preZ  , data=data_LTLE,na.action= na.omit))

# Make a copy of residuals
residuals_bin <- List15_12mZ_change$residuals

# Set all elements to 0
residuals_bin <- rep(0, length(residuals_bin))

residuals_bin[List15_12mZ_change$residuals <= (quantile(List15_12mZ_change$residuals,0.20))] <- -1

# Set elements to -1 where residuals are less than -1.5 standard deviations
residuals_bin[List15_12mZ_change$residuals >= (quantile(List15_12mZ_change$residuals,0.80))] <- 1

# Get the index of non-missing values in the 'List15_3mZ_change' column
non_missing_index <- !is.na(data_LTLE$List15_12mZ_change)

# Place the residuals back into the dataframe at the non-missing index
data_LTLE$List15_12mZ_change_residuals_bin <- NA  # Initialize a new column for residuals
data_LTLE$List15_12mZ_change_residuals_bin[non_missing_index] <- residuals_bin
data_LTLE$List15_12mZ_change_residuals <- NA  # Initialize a new column for residuals
data_LTLE$List15_12mZ_change_residuals[non_missing_index] <- List15_12mZ_change$residuals
```
## Verbal Retrieval
```{r}
library(RobStatTM)
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#3 months 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

summary( ListA6_3mZ_change <- lmrobdetMM(ListA6_3mZ_change ~ Age + ResectinMask_Scaled +  ListA6_preZ  , data=data_LTLE,na.action= na.omit))

# Make a copy of residuals
residuals_bin <- ListA6_3mZ_change$residuals

# Set all elements to 0
residuals_bin <- rep(0, length(residuals_bin))


# Set elements to 1 where residuals are greater than 1.5 standard deviations
residuals_bin[ListA6_3mZ_change$residuals <= (quantile(ListA6_3mZ_change$residuals,0.20))] <- -1

# Set elements to -1 where residuals are less than -1.5 standard deviations
residuals_bin[ListA6_3mZ_change$residuals >= (quantile(ListA6_3mZ_change$residuals,0.80))] <- 1

# Get the index of non-missing values in the 'ListA6_3mZ_change' column
non_missing_index <- !is.na(data_LTLE$ListA6_3mZ_change)

# Place the residuals back into the dataframe at the non-missing index
data_LTLE$ListA6_3mZ_change_residuals_bin <- NA  # Initialize a new column for residuals
data_LTLE$ListA6_3mZ_change_residuals_bin[non_missing_index] <- residuals_bin
data_LTLE$ListA6_3mZ_change_residuals <- NA  # Initialize a new column for residuals
data_LTLE$ListA6_3mZ_change_residuals[non_missing_index] <- ListA6_3mZ_change$residuals
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#12 months 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
summary( ListA6_12mZ_change <- lmrobdetMM(ListA6_12mZ_change ~ Age + ResectinMask_Scaled +  ListA6_preZ  , data=data_LTLE,na.action= na.omit))

# Make a copy of residuals
residuals_bin <- ListA6_12mZ_change$residuals

# Set all elements to 0
residuals_bin <- rep(0, length(residuals_bin))

residuals_bin[ListA6_12mZ_change$residuals <= (quantile(ListA6_12mZ_change$residuals,0.20))] <- -1

# Set elements to -1 where residuals are less than -1.5 standard deviations
residuals_bin[ListA6_12mZ_change$residuals >= (quantile(ListA6_12mZ_change$residuals,0.80))] <- 1

# Get the index of non-missing values in the 'ListA6_3mZ_change' column
non_missing_index <- !is.na(data_LTLE$ListA6_12mZ_change)

# Place the residuals back into the dataframe at the non-missing index
data_LTLE$ListA6_12mZ_change_residuals_bin <- NA  # Initialize a new column for residuals
data_LTLE$ListA6_12mZ_change_residuals_bin[non_missing_index] <- residuals_bin
data_LTLE$ListA6_12mZ_change_residuals <- NA  # Initialize a new column for residuals
data_LTLE$ListA6_12mZ_change_residuals[non_missing_index] <- ListA6_12mZ_change$residuals


```


# Descriptive Statistics 
## Three Cohort Differences
```{r}
#Extract data 
data_atlas <- data_LTLE[data_LTLE$Analysis_Atlas == 1, ]
data_preop <- data_LTLE[data_LTLE$Analaysis_preop == 1, ]
data_postop <- data_LTLE[data_LTLE$Analysis_postop == 1, ]

#Label data 
data_atlas$source <- "atlas"
data_preop$source <- "preop"
data_postop$source <- "postop"

# Stack the dataframes together
combined_data <- rbind(data_atlas, data_preop, data_postop)

#ONSET AGE
cat(sprintf("%.2f (%.2f)", mean(data_atlas$OnsetAge), sd(data_atlas$OnsetAge)))
cat(sprintf("%.2f (%.2f)", mean(data_preop$OnsetAge), sd(data_preop$OnsetAge)))
cat(sprintf("%.2f (%.2f)", mean(data_postop$OnsetAge), sd(data_postop$OnsetAge)))
#Anova
summary(anova_result <- aov(OnsetAge ~ source, data = combined_data))


#AGE
cat(sprintf("%.2f (%.2f)", mean(data_atlas$Age), sd(data_atlas$Age)))
cat(sprintf("%.2f (%.2f)", mean(data_preop$Age), sd(data_preop$Age)))
cat(sprintf("%.2f (%.2f)", mean(data_postop$Age), sd(data_postop$Age)))
#Anova
summary(anova_result <- aov(Age ~ source, data = combined_data))

#EpLength
cat(sprintf("%.2f (%.2f)", mean(data_atlas$EpLength), sd(data_atlas$EpLength)))
cat(sprintf("%.2f (%.2f)", mean(data_preop$EpLength), sd(data_preop$EpLength)))
cat(sprintf("%.2f (%.2f)", mean(data_postop$EpLength), sd(data_postop$EpLength)))
#Anova
summary(anova_result <- aov(EpLength ~ source, data = combined_data))

#Pathology
crosstab_HS<- table(combined_data$source, combined_data$HS_bin)
crosstab_HS_percent <- prop.table(crosstab_HS, margin = 1) * 100
summary(crosstab_HS_percent)
```

# Neuropsychology 
```{r}
#Preop Mean / STD 
mean(data_LTLE$List15_preZ, na.rm = TRUE)
sd(data_LTLE$List15_preZ, na.rm = TRUE)

#3m Mean / STD 
mean(data_LTLE$List15_3mZ, na.rm = TRUE)
sd(data_LTLE$List15_3mZ, na.rm = TRUE)

#12m Mean / STD 
mean(data_LTLE$List15_12mZ, na.rm = TRUE)
sd(data_LTLE$List15_12mZ, na.rm = TRUE)

ListA15_long_z <- melt(data_LTLE, 
                    id.vars = c("IDP","Age", "ResectionvMask","OnsetAge","EpLength"),
                    measure.vars = c("List15_preZ", "List15_3mZ", "List15_12mZ"), 
                    variable.name = "Timepoint",
                    value.name = "ListA15_outcome")

ListA15_long_z <- na.omit(ListA15_long_z)


anova_result <- aov(ListA15_outcome ~ Timepoint + Age + OnsetAge +EpLength+ ResectionvMask + Error(IDP/Timepoint), data = ListA15_long_z)
summary(anova_result)
pairwise.t.test(ListA15_long_z$ListA15_outcome, ListA15_long_z$Timepoint, p.adjust.method = "bonferroni")


# List A6
ListA6_long_z <- melt(data_LTLE, 
                    id.vars = c("IDP","Age", "ResectionvMask","OnsetAge","EpLength"),
                    measure.vars = c("ListA6_preZ", "ListA6_3mZ", "ListA6_12mZ"), 
                    variable.name = "Timepoint",
                    value.name = "ListA6_outcome")

ListA6_long_z <- na.omit(ListA6_long_z)

anova_result <- aov(ListA6_outcome ~ Timepoint + Age + OnsetAge +EpLength+ ResectionvMask + Error(IDP/Timepoint), data = ListA6_long_z)
summary(anova_result)
pairwise.t.test(ListA6_long_z$ListA6_outcome, ListA6_long_z$Timepoint, p.adjust.method = "bonferroni")
```

#Atlas Based Analysis 
## SoZ Outcome 
```{r}
#SoZ Outcome
#FNX
crosstab_SoZ <- table(data_LTLE$TLSM_FNX_bin, data_LTLE$ILAE_bin)
summary(crosstab_SoZ)
row_sums <- rowSums(crosstab_SoZ)
# Calculate the percentages for each group
crosstab_SoZ_percent <- prop.table(crosstab_SoZ, margin = 1) * 100
# Print the percentage table
print(crosstab_SoZ_percent)
summary(crosstab_SoZ_percent)

#vCing
crosstab_SoZ <- table(data_LTLE$TLSM_vCing_bin, data_LTLE$ILAE_bin)
summary(crosstab_SoZ)
row_sums <- rowSums(crosstab_SoZ)
# Calculate the percentages for each group
crosstab_SoZ_percent <- prop.table(crosstab_SoZ, margin = 1) * 100
# Print the percentage table
print(crosstab_SoZ_percent)
summary(crosstab_SoZ_percent)
```

## Verbal Encoding 
```{r}
#Setup long data format
ListA15_long_z <- melt(data_LTLE, 
                    id.vars = c("IDP","TLSM_vCing_bin","TLSM_FNX_bin","ILAE_bin"),
                    measure.vars = c("List15_3mZ_change_residuals_bin","List15_12mZ_change_residuals_bin"), 
                    variable.name = "Timepoint",
                    value.name = "ListA15_RCI")

ListA15_long_z <- na.omit(ListA15_long_z)

ListA15_long_z$Timepoint <- as.character(ListA15_long_z$Timepoint)
ListA15_long_z$Timepoint <- ifelse(ListA15_long_z$Timepoint == "List15_3mZ_change_residuals_bin", "Postop3m", ListA15_long_z$Timepoint)
ListA15_long_z$Timepoint <- ifelse(ListA15_long_z$Timepoint == "List15_12mZ_change_residuals_bin", "Postop_12m", ListA15_long_z$Timepoint)

#FNX
crosstab_ListA15 <- table(ListA15_long_z$TLSM_FNX_bin, ListA15_long_z$ListA15_RCI)
row_sums <- rowSums(crosstab_ListA15)

# Calculate the percentages for each group
crosstab_ListA15_percent <- prop.table(crosstab_ListA15, margin = 1) * 100

# Print the percentage table
print(crosstab_ListA15_percent)
summary(crosstab_ListA15_percent)


#vCing
crosstab_ListA15 <- table(ListA15_long_z$TLSM_vCing_bin, ListA15_long_z$ListA15_RCI)
summary(crosstab_ListA15)

row_sums <- rowSums(crosstab_ListA15)

# Calculate the percentages for each group
crosstab_ListA15_percent <- prop.table(crosstab_ListA15, margin = 1) * 100

# Print the percentage table
print(crosstab_ListA15_percent)
summary(crosstab_ListA15_percent)


```
## Verbal Retrieval 
```{r}
#Setup long data format
ListA6_long_z <- melt(data_LTLE, 
                    id.vars = c("IDP","TLSM_vCing_bin","TLSM_FNX_bin"),
                    measure.vars = c("ListA6_3mZ_change_residuals_bin","ListA6_12mZ_change_residuals_bin"), 
                    variable.name = "Timepoint",
                    value.name = "ListA6_RCI")

ListA6_long_z <- na.omit(ListA6_long_z)

ListA6_long_z$Timepoint <- as.character(ListA6_long_z$Timepoint)
ListA6_long_z$Timepoint <- ifelse(ListA6_long_z$Timepoint == "ListA6_3mZ_change_residuals_bin", "Postop3m", ListA6_long_z$Timepoint)
ListA6_long_z$Timepoint <- ifelse(ListA6_long_z$Timepoint == "ListA6_12mZ_change_residuals_bin", "Postop_12m", ListA6_long_z$Timepoint)

#FNX
crosstab_ListA6 <- table(ListA6_long_z$TLSM_FNX_bin, ListA6_long_z$ListA6_RCI)
row_sums <- rowSums(crosstab_ListA6)

# Calculate the percentages for each group
crosstab_ListA6_percent <- prop.table(crosstab_ListA6, margin = 1) * 100

# Print the percentage table
print(crosstab_ListA6_percent)
summary(crosstab_ListA6_percent)


#vCing
crosstab_ListA6 <- table(ListA6_long_z$TLSM_vCing_bin, ListA6_long_z$ListA6_RCI)
summary(crosstab_ListA6)

row_sums <- rowSums(crosstab_ListA6)

# Calculate the percentages for each group
crosstab_ListA6_percent <- prop.table(crosstab_ListA6, margin = 1) * 100

# Print the percentage table
print(crosstab_ListA6_percent)
summary(crosstab_ListA6_percent)
```

#Preoperative Tractography Transection 
## Seizure Outcome 
```{r}
t.test(Tractography_vCing_scaled ~ ILAE_bin, data=data_LTLE)
t.test(Tractography_FNX_scaled ~ ILAE_bin, data=data_LTLE)
```
## Setup Dataframe 
```{r}
#Setup long dataframe 
ListA15_resect_LTLE <- melt(data_LTLE, 
                    id.vars = c("IDP","Tractography_vCing_scaled","ResectinMask_Scaled","Type","EpLength","Tractography_FNX_scaled","OnsetAge","List15_preZ","Age"),
                    measure.vars = c("List15_3mZ_change", "List15_12mZ_change"), 
                    variable.name = "Timepoint",
                    value.name = "ListA15_changeZ")

ListA6_resect_LTLE <- melt(data_LTLE, 
                    id.vars = c("IDP","TLE_side","Tractography_vCing_scaled","ResectinMask_Scaled","Type","EpLength","Tractography_FNX_scaled","OnsetAge","ListA6_preZ","Age"),
                    measure.vars = c("ListA6_3mZ_change", "ListA6_12mZ_change"), 
                    variable.name = "Timepoint",
                    value.name = "ListA6_changeZ")

```
## Preop Tracts, Fornix, Verbal Encoding 
```{r}
#FORNIX Linear Mixed Effect Model
summary( mdl_null <- lmer(ListA15_changeZ ~ Timepoint + Age+ List15_preZ +ResectinMask_Scaled+Type+ (1|IDP), data=subset(ListA15_resect_LTLE, !is.na(Tractography_FNX_scaled))))
summary( mdl_FNX <- lmer(ListA15_changeZ ~ Timepoint + List15_preZ+ Tractography_FNX_scaled+ Age +Type+ ResectinMask_Scaled+ (1|IDP), data=subset(ListA15_resect_LTLE, !is.na(Tractography_FNX_scaled))))
mdl_FNX_anova <- anova(mdl_FNX,mdl_null)
mdl_FNX_conf <- confint(mdl_FNX,level = 0.95)

# Code to print easy-to-copy stuff for paper 
mdl_FNX_summary <- summary(mdl_FNX)
conf_intervals <- mdl_FNX_conf[rownames(mdl_FNX_summary$coefficients), ]
covariate_names <- rownames(mdl_FNX_summary$coefficients)
for (i in 1:nrow(mdl_FNX_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_FNX_summary$coefficients[i, "Estimate"]
  p_value <- mdl_FNX_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_FNX_anova$Df[2], mdl_FNX_anova$Chisq[2], mdl_FNX_anova$`Pr(>Chisq)`[2]))
#/ 
```
## Fornix without Resection Volume
```{r}

#FORNIX Linear Mixed Effect Model
summary( mdl_null <- lmer(ListA15_changeZ ~ Timepoint + Age+ List15_preZ +Type+ (1|IDP), data=subset(ListA15_resect_LTLE, !is.na(Tractography_FNX_scaled))))
summary( mdl_FNX <- lmer(ListA15_changeZ ~ Timepoint + List15_preZ+ Tractography_FNX_scaled+ Age +Type+ (1|IDP), data=subset(ListA15_resect_LTLE, !is.na(Tractography_FNX_scaled))))
mdl_FNX_anova <- anova(mdl_FNX,mdl_null)
mdl_FNX_conf <- confint(mdl_FNX,level = 0.95)

# Code to print easy-to-copy stuff for paper 
mdl_FNX_summary <- summary(mdl_FNX)
conf_intervals <- mdl_FNX_conf[rownames(mdl_FNX_summary$coefficients), ]
covariate_names <- rownames(mdl_FNX_summary$coefficients)
for (i in 1:nrow(mdl_FNX_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_FNX_summary$coefficients[i, "Estimate"]
  p_value <- mdl_FNX_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_FNX_anova$Df[2], mdl_FNX_anova$Chisq[2], mdl_FNX_anova$`Pr(>Chisq)`[2]))
#/ 

```

## Preop Tracts, Ventral Cingulum , Verbal Encoding 
```{r}
#vCing
summary( mdl_null <- lmer(ListA15_changeZ ~ Timepoint + Age+ List15_preZ +ResectinMask_Scaled+Type+ (1|IDP), data=subset(ListA15_resect_LTLE, !is.na(Tractography_vCing_scaled))))
summary( mdl_vCing <- lmer(ListA15_changeZ ~ Timepoint + Age + List15_preZ+ Tractography_vCing_scaled+ Type+ ResectinMask_Scaled+ (1|IDP), data=subset(ListA15_resect_LTLE, !is.na(Tractography_vCing_scaled))))
mdl_vCing_anova <- anova(mdl_vCing,mdl_null)
mdl_vCing_conf <- confint(mdl_vCing,level = 0.95)

# Code to print easy-to-copy stuff for paper 
mdl_vCing_summary <- summary(mdl_vCing)
conf_intervals <- mdl_vCing_conf[rownames(mdl_vCing_summary$coefficients), ]
covariate_names <- rownames(mdl_vCing_summary$coefficients)

for (i in 1:nrow(mdl_vCing_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_vCing_summary$coefficients[i, "Estimate"]
  p_value <- mdl_vCing_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_vCing_anova$Df[2], mdl_vCing_anova$Chisq[2], mdl_vCing_anova$`Pr(>Chisq)`[2]))
#/
```

## Preop Tracts, Fornix, Verbal Encoding 
```{r}

#FNX
summary( mdl_null <- lmer(ListA6_changeZ ~ Timepoint + Age+ ListA6_preZ +ResectinMask_Scaled+Type+ (1|IDP), data=subset(ListA6_resect_LTLE, !is.na(Tractography_FNX_scaled))))
summary( mdl_FNX <- lmer(ListA6_changeZ ~ Timepoint + ListA6_preZ+ Tractography_FNX_scaled+ Age +Type+ ResectinMask_Scaled+ (1|IDP), data=subset(ListA6_resect_LTLE, !is.na(Tractography_FNX_scaled))))
mdl_FNX_anova <- anova(mdl_FNX,mdl_null)
mdl_FNX_conf <- confint(mdl_FNX,level = 0.95)
#For paper
mdl_FNX_summary <- summary(mdl_FNX)
conf_intervals <- mdl_FNX_conf[rownames(mdl_FNX_summary$coefficients), ]
covariate_names <- rownames(mdl_FNX_summary$coefficients)

for (i in 1:nrow(mdl_FNX_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_FNX_summary$coefficients[i, "Estimate"]
  p_value <- mdl_FNX_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_FNX_anova$Df[2], mdl_FNX_anova$Chisq[2], mdl_FNX_anova$`Pr(>Chisq)`[2]))

```
### Simplified Models (without resection volume)
```{r}
#FNX
summary( mdl_null <- lmer(ListA6_changeZ ~ Timepoint + Age+ ListA6_preZ +Type+ (1|IDP), data=subset(ListA6_resect_LTLE, !is.na(Tractography_FNX_scaled))))
summary( mdl_FNX <- lmer(ListA6_changeZ ~ Timepoint + ListA6_preZ+ Tractography_FNX_scaled+ Age +Type+ (1|IDP), data=subset(ListA6_resect_LTLE, !is.na(Tractography_FNX_scaled))))
mdl_FNX_anova <- anova(mdl_FNX,mdl_null)
mdl_FNX_conf <- confint(mdl_FNX,level = 0.95)
#For paper
mdl_FNX_summary <- summary(mdl_FNX)
conf_intervals <- mdl_FNX_conf[rownames(mdl_FNX_summary$coefficients), ]
covariate_names <- rownames(mdl_FNX_summary$coefficients)

for (i in 1:nrow(mdl_FNX_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_FNX_summary$coefficients[i, "Estimate"]
  p_value <- mdl_FNX_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_FNX_anova$Df[2], mdl_FNX_anova$Chisq[2], mdl_FNX_anova$`Pr(>Chisq)`[2]))

```


## Preop Tracts, Ventral Cingulum , Verbal Encoding 
```{r}
#vCing
summary( mdl_null <- lmer(ListA6_changeZ ~ Timepoint + Age+ ListA6_preZ +ResectinMask_Scaled+Type+ (1|IDP), data=subset(ListA6_resect_LTLE, !is.na(Tractography_vCing_scaled))))
summary( mdl_vCing <- lmer(ListA6_changeZ ~ Timepoint + Age + ListA6_preZ+ Tractography_vCing_scaled+ Type+ ResectinMask_Scaled+ (1|IDP), data=subset(ListA6_resect_LTLE, !is.na(Tractography_vCing_scaled))))
mdl_vCing_anova <- anova(mdl_vCing,mdl_null)
mdl_vCing_conf <- confint(mdl_vCing,level = 0.95)
#For paper
mdl_vCing_summary <- summary(mdl_vCing)
conf_intervals <- mdl_vCing_conf[rownames(mdl_vCing_summary$coefficients), ]
covariate_names <- rownames(mdl_vCing_summary$coefficients)

for (i in 1:nrow(mdl_vCing_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_vCing_summary$coefficients[i, "Estimate"]
  p_value <- mdl_vCing_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_vCing_anova$Df[2], mdl_vCing_anova$Chisq[2], mdl_vCing_anova$`Pr(>Chisq)`[2]))
```
### Simplified Model (Without resection Volume)
```{r}
#vCing
summary( mdl_null <- lmer(ListA6_changeZ ~ Timepoint + Age+ ListA6_preZ +Type+ (1|IDP), data=subset(ListA6_resect_LTLE, !is.na(Tractography_vCing_scaled))))
summary( mdl_vCing <- lmer(ListA6_changeZ ~ Timepoint + Age + ListA6_preZ+ Tractography_vCing_scaled+ Type+ (1|IDP), data=subset(ListA6_resect_LTLE, !is.na(Tractography_vCing_scaled))))
mdl_vCing_anova <- anova(mdl_vCing,mdl_null)
mdl_vCing_conf <- confint(mdl_vCing,level = 0.95)
#For paper
mdl_vCing_summary <- summary(mdl_vCing)
conf_intervals <- mdl_vCing_conf[rownames(mdl_vCing_summary$coefficients), ]
covariate_names <- rownames(mdl_vCing_summary$coefficients)

for (i in 1:nrow(mdl_vCing_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_vCing_summary$coefficients[i, "Estimate"]
  p_value <- mdl_vCing_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_vCing_anova$Df[2], mdl_vCing_anova$Chisq[2], mdl_vCing_anova$`Pr(>Chisq)`[2]))
```

# Postoperative Volume Analysis
## Verbal Encoding 
### Setup Dataframe 
```{r}
ListA15_vol_LTLE <- melt(data_LTLE, 
                    id.vars = c("IDP","TLE_side","Postop_vol_vCing_scaled","ResectinMask_Scaled","Type","EpLength","Postop_vol_FNX_scaled","OnsetAge","List15_preZ","Age","Scanner"),
                    measure.vars = c("List15_3mZ_change", "List15_12mZ_change"), 
                    variable.name = "Timepoint",
                    value.name = "ListA15_changeZ")
```
### Fornix Analysis
```{r}
#FNX
summary( mdl_null <- lmer(ListA15_changeZ ~ Timepoint + Age+ List15_preZ +ResectinMask_Scaled+Type+ Scanner+(1|IDP), data=subset(ListA15_vol_LTLE, !is.na(Postop_vol_FNX_scaled))))
summary( mdl_FNX <- lmer(ListA15_changeZ ~ Timepoint + List15_preZ+ Postop_vol_FNX_scaled+ Age +Type+ ResectinMask_Scaled+Scanner+ (1|IDP), data=subset(ListA15_vol_LTLE, !is.na(Postop_vol_FNX_scaled))))
mdl_FNX_anova <- anova(mdl_FNX,mdl_null)
mdl_FNX_conf <- confint(mdl_FNX,level = 0.95)
#For paper
mdl_FNX_summary <- summary(mdl_FNX)
conf_intervals <- mdl_FNX_conf[rownames(mdl_FNX_summary$coefficients), ]
covariate_names <- rownames(mdl_FNX_summary$coefficients)

for (i in 1:nrow(mdl_FNX_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_FNX_summary$coefficients[i, "Estimate"]
  p_value <- mdl_FNX_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_FNX_anova$Df[2], mdl_FNX_anova$Chisq[2], mdl_FNX_anova$`Pr(>Chisq)`[2]))
```
### Ventral Cingulum 
```{r}
#vCing
summary( mdl_null <- lmer(ListA15_changeZ ~ Timepoint + Age+ List15_preZ +ResectinMask_Scaled+Type+ (1|IDP), data=subset(ListA15_vol_LTLE, !is.na(Postop_vol_vCing_scaled))))
summary( mdl_vCing <- lmer(ListA15_changeZ ~ Timepoint + List15_preZ+ Postop_vol_vCing_scaled+Age +  Type+ ResectinMask_Scaled+ (1|IDP), data=subset(ListA15_vol_LTLE, !is.na(Postop_vol_vCing_scaled))))
mdl_vCing_anova <- anova(mdl_vCing,mdl_null)
mdl_vCing_conf <- confint(mdl_vCing,level = 0.95)
#For paper
mdl_vCing_summary <- summary(mdl_vCing)
conf_intervals <- mdl_vCing_conf[rownames(mdl_vCing_summary$coefficients), ]
covariate_names <- rownames(mdl_vCing_summary$coefficients)

for (i in 1:nrow(mdl_vCing_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_vCing_summary$coefficients[i, "Estimate"]
  p_value <- mdl_vCing_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_vCing_anova$Df[2], mdl_vCing_anova$Chisq[2], mdl_vCing_anova$`Pr(>Chisq)`[2]))
```
#### Simplified (No resection volume)

## Verbal Retrieval
### Dataframe setup  
```{r}
ListA6_vol_LTLE <- melt(data_LTLE, 
                    id.vars = c("IDP","TLE_side","Postop_vol_vCing_scaled","ResectinMask_Scaled","Type","EpLength","Postop_vol_FNX_scaled","OnsetAge","ListA6_preZ","Age","Scanner"),
                    measure.vars = c("ListA6_3mZ_change", "ListA6_12mZ_change"), 
                    variable.name = "Timepoint",
                    value.name = "ListA6_changeZ")

```
### Fornix 
```{r}
#FNX
summary( mdl_null <- lmer(ListA6_changeZ ~ Timepoint + Age+ ListA6_preZ +ResectinMask_Scaled+Type+ (1|IDP), data=subset(ListA6_vol_LTLE, !is.na(Postop_vol_FNX_scaled))))
summary( mdl_FNX <- lmer(ListA6_changeZ ~ Timepoint + ListA6_preZ+ Postop_vol_FNX_scaled+ Age +Type+ ResectinMask_Scaled+ (1|IDP), data=subset(ListA6_vol_LTLE, !is.na(Postop_vol_FNX_scaled))))
mdl_FNX_anova <- anova(mdl_FNX,mdl_null)
mdl_FNX_conf <- confint(mdl_FNX,level = 0.95)
#For paper
mdl_FNX_summary <- summary(mdl_FNX)
conf_intervals <- mdl_FNX_conf[rownames(mdl_FNX_summary$coefficients), ]
covariate_names <- rownames(mdl_FNX_summary$coefficients)

for (i in 1:nrow(mdl_FNX_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_FNX_summary$coefficients[i, "Estimate"]
  p_value <- mdl_FNX_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_FNX_anova$Df[2], mdl_FNX_anova$Chisq[2], mdl_FNX_anova$`Pr(>Chisq)`[2]))

```
#### Simplied model without reseciton vlume 
```{r}
#FNX
summary( mdl_null <- lmer(ListA6_changeZ ~ Timepoint + Age+ ListA6_preZ +Type+ (1|IDP), data=subset(ListA6_vol_LTLE, !is.na(Postop_vol_FNX_scaled))))
summary( mdl_FNX <- lmer(ListA6_changeZ ~ Timepoint + ListA6_preZ+ Postop_vol_FNX_scaled+ Age +Type+ (1|IDP), data=subset(ListA6_vol_LTLE, !is.na(Postop_vol_FNX_scaled))))
mdl_FNX_anova <- anova(mdl_FNX,mdl_null)
mdl_FNX_conf <- confint(mdl_FNX,level = 0.95)
#For paper
mdl_FNX_summary <- summary(mdl_FNX)
conf_intervals <- mdl_FNX_conf[rownames(mdl_FNX_summary$coefficients), ]
covariate_names <- rownames(mdl_FNX_summary$coefficients)

for (i in 1:nrow(mdl_FNX_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_FNX_summary$coefficients[i, "Estimate"]
  p_value <- mdl_FNX_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_FNX_anova$Df[2], mdl_FNX_anova$Chisq[2], mdl_FNX_anova$`Pr(>Chisq)`[2]))

```
### Ventral Cingulum
```{r}
summary( mdl_null <- lmer(ListA6_changeZ ~ Timepoint + Age+ ListA6_preZ +ResectinMask_Scaled+Type+ (1|IDP), data=subset(ListA6_vol_LTLE, !is.na(Postop_vol_vCing_scaled))))
summary( mdl_vCing <- lmer(ListA6_changeZ ~ Timepoint + ListA6_preZ+ Postop_vol_vCing_scaled+Age +  Type+ ResectinMask_Scaled+ (1|IDP), data=subset(ListA6_vol_LTLE, !is.na(Postop_vol_vCing_scaled))))
mdl_vCing_anova <- anova(mdl_vCing,mdl_null)
mdl_vCing_conf <- confint(mdl_vCing,level = 0.95)
#For paper
mdl_vCing_summary <- summary(mdl_vCing)
conf_intervals <- mdl_vCing_conf[rownames(mdl_vCing_summary$coefficients), ]
covariate_names <- rownames(mdl_vCing_summary$coefficients)

for (i in 1:nrow(mdl_vCing_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_vCing_summary$coefficients[i, "Estimate"]
  p_value <- mdl_vCing_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_vCing_anova$Df[2], mdl_vCing_anova$Chisq[2], mdl_vCing_anova$`Pr(>Chisq)`[2]))
```
#### SImplified Model
```{r}
summary( mdl_null <- lmer(ListA6_changeZ ~ Timepoint + Age+ ListA6_preZ +Type+ (1|IDP), data=subset(ListA6_vol_LTLE, !is.na(Postop_vol_vCing_scaled))))
summary( mdl_vCing <- lmer(ListA6_changeZ ~ Timepoint + ListA6_preZ+ Postop_vol_vCing_scaled+Age +  Type+ (1|IDP), data=subset(ListA6_vol_LTLE, !is.na(Postop_vol_vCing_scaled))))
mdl_vCing_anova <- anova(mdl_vCing,mdl_null)
mdl_vCing_conf <- confint(mdl_vCing,level = 0.95)
#For paper
mdl_vCing_summary <- summary(mdl_vCing)
conf_intervals <- mdl_vCing_conf[rownames(mdl_vCing_summary$coefficients), ]
covariate_names <- rownames(mdl_vCing_summary$coefficients)

for (i in 1:nrow(mdl_vCing_summary$coefficients)) {
  covariate_name <- covariate_names[i]
  estimate <- mdl_vCing_summary$coefficients[i, "Estimate"]
  p_value <- mdl_vCing_summary$coefficients[i, "Pr(>|t|)"]
  conf_low <- conf_intervals[i, 1]
  conf_high <- conf_intervals[i, 2]
  
  cat(sprintf("Name: %s, Estimate = %.3f, p = %.3f, 95CI = %.3f:%.3f\n", covariate_name, estimate, p_value, conf_low, conf_high))
}
cat(sprintf("X(%.0f)=%.3f, p = %.3f", mdl_vCing_anova$Df[2], mdl_vCing_anova$Chisq[2], mdl_vCing_anova$`Pr(>Chisq)`[2]))
```
## Seizure Outcome 
```{r}
t.test(Postop_vol_FNX ~ ILAE_bin, data=data_LTLE)
t.test(Postop_vol_vCing ~ ILAE_bin, data=data_LTLE)
```






